Parallel-in-time methods for Particle Simulations

### 2024-11-30 paper/main.tex
Job edits

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[thinc]{esdiff}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=\linewidth]{fig_1.eps}}
\caption{Parareal convergence for the example of a harmonic oscillator. The coarse solver is Euler and the fine solver is RK4}
\label{fig}
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=\linewidth]{fig_2.eps}}
\caption{Path of Mercury over the time of one Earth year in the simulation converging over multiple iterations of the parareal algorithm. Velocity verlet and RK4 are used with the same step size of $0.5\text{day}$.}
\label{fig}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=\linewidth]{fig_3.eps}}
\caption{\color{red} TODO}
\label{fig}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=\linewidth]{fig_4.eps}}
\caption{\color{red} TODO}
\label{fig}
\end{figure}

>>>>

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[thinc]{esdiff}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=\linewidth]{fig_1.eps}}
\caption{Parareal convergence for the example of a harmonic oscillator. The coarse solver is Euler and the fine solver is RK4}
\label{oscillator}
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=\linewidth]{fig_2.eps}}
\caption{Path of Mercury over the time of one Earth year in the simulation converging over multiple iterations of the parareal algorithm. Velocity verlet and RK4 are used with the same step size of $0.5\text{day}$.}
\label{mercury}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=\linewidth]{fig_3.eps}}
\caption{\color{red} TODO}
\label{longrunning}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=\linewidth]{fig_4.eps}}
\caption{\color{red} TODO}
\label{energy}
\end{figure}

\begin{table*}[htbp]
\caption{Comparison of running times taken by different configurations of the simulator}
\begin{center}
\begin{tabular}{ccrrrrrrcc}
\toprule
\textbf{Program} & \textbf{Environment} & \textbf{n CPUs} & \textbf{Segments} & \textbf{Fine steps} & \textbf{Coarse steps} & \textbf{Final steps} & \textbf{CPU time} & \textbf{Runtime} \\
\midrule
parareal & MetaCentrum & 30 & 30 & $10^5$ & 100 & $30\cdot 10^5$ & 02:01:57 & 00:04:30 \\
serial   & MetaCentrum &  1 &  1 & N/A    & N/A & $30\cdot 10^5$ & 00:06:27 & 00:06:27 \\
parareal & Laptop      &  4 &  4 & $10^5$ & 100 & $4\cdot 10^5$ & 00:03:26 & 00:00:51 \\
serial   & Laptop      &  1 &  1 & N/A    & N/A & $4\cdot 10^5$ & 00:00:30 & 00:00:30 \\
\bottomrule
\end{tabular}
\label{runtimes}
\end{center}
\end{table*}
